---
title: "Alcohol vs Seat choice"
author: " Alexis Velasco"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Based on the box plot those who sit in the back row seem to consume more alcohol than the middle and front rows. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The mean or those sitting in the back who have consumed alcohol 9.62. Almost three times as much as the middle seats who average out to a mean of 3.28. Not coming close to the front row only having a mean of 1.8 consumption rate of alcohol. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The anova has a significantly small result a tukey should be the following step. 

```{r}
plot(TukeyHSD(model1))
```
The middle-front and front-back have confidence intervals are less than zero, it can be assured the results are vastly different.

## Conclusions

After reviewing the data it can be concluded that the people in the back row drank the most alcohol giving them the highest mean of 9.62, despite being the smallest amount of people. The middle row has 83 people and the front row has 33 people but both still had a mean lower than the back row. 
