---
title: "Alcohol vs Seat choice"
author: " Alexis Velasco"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Based on the box plot those who sit in the back row seem to consume more alcohol than the middle and front rows. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The mean or those sitting in the back who have consumed alcohol 9.62. Almost three times as much as the middle seats who average out to a mean of 3.28. Not coming close to the front row only having a mean of 1.8 consumption rate of alcohol. 

## Inferential Tests

## Conclusions


